PK object batch mode trial

### 2023-06-08 data-raw/batchMode_trial_gpm.Rmd
Generated a "wide" data.frame for the fit summaries that could perhaps be used in some downstream analyses.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj branch
library(tidyverse)
library(here)
```

@@

```{r data_loading}
cvt %>% names()

cvt %>% pull(chemicals_analyzed.dsstox_substance_id) %>% unique() %>% length()

@@

```{r}
my_pk <- pk(data = my_predata) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = "L-BFGS-B") +
  scale_conc(dose_norm = TRUE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

@@

my_pk <- data_info(my_pk)

@@

my_pk <- fit(my_pk)

pk_results <- coef(my_pk)

predict(my_pk) # Doesn't run rn for some reason
pred_results <- predict(my_pk)

plot_results <- plot(my_pk)
print(plot_results)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)

library(tidyverse, quietly = TRUE)
devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj branch

@@

The first step is understanding how to work with a single DTXSID + Species combination.
Once we know how to do this, it will be easier to apply it to (potentially)
a list of these objects in a vectorized fashion.
Here I subset the `cvt` object and use that as my working data.

```{r data_loading}
# There are 103 unique chemicals in this object
cvt %>% pull(chemicals_analyzed.dsstox_substance_id) %>% unique() %>% length()

@@

Next, I want to follow the steps required for the particular analysis I would like.
In this instance, I set the optimizer to "L-BFGS-B" and dose-normalize the output.
I do not scale the time or log-transform the concentration values.
Since I would like to do a "Pooled" analysis,
I set the `error_group = vars(Chemical, Species)`.

```{r single_fit}
my_pk <- pk(data = my_predata) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = "L-BFGS-B") +
  scale_conc(dose_norm = TRUE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

@@

my_pk <- data_info(my_pk) # summarize error (Returning more or less than 1 row per summarize)

@@

my_pk <- fit(my_pk)
```

```{r single_result_extraction}
# A list of each fit model with the estimated parameters for that model
# Each row has 
pk_results <- coef(my_pk)

pred_results <- predict(my_pk)

plot_results <- plot(my_pk)

@@

```{r single_result_tidying}
# Currently, it seems tk_stats_*() does not return dose-normalized values.
my_tkstats %>%
  pluck("model_1comp") %>%
  distinct() %>% head()

# Assembling the data that I want to add for a summary data.frame
my_pk$fit$model_flat
my_pk$settings_optimx$method
my_pk$scales$conc$dose_norm
my_pk$scales$conc$log10_trans
rlang::quo_get_expr(my_pk$scales$conc$expr)

# Building the wide "fit" data.frame from various parts of the `pk` object
my_pk$fit %>%
  as.data.frame() %>%
  # Switches default order of 
  rename_with(~paste0(str_extract(.,
                                  pattern = "(?<=\\.).+$"),
                      ".",
                      str_extract(.,
                                  pattern = "(?<=model_)[:alnum:]+")
                      )
  ) %>%
  dplyr::select(-(starts_with(c("kkt", "xtime", "niter", "fevals", "gevals", "sigma")))) %>%
  rownames_to_column(var = "method") %>%
  mutate(DTXSID = unique(my_pk$data$DTXSID),
         Species = unique(my_pk$data$Species),
         fit_log_conc = my_pk$scales$conc$log10_trans,
         fit_conc_dose = my_pk$scales$conc$dose_norm,
         rescale_time = ifelse(my_pk$scales$time == "identity",
                               FALSE, TRUE),
         .before = method) %>%
  View()
